Spfy: distributed predictive genomics of E.coli with graph based result linkage

### 2017-08-21 paper-webserver.tex
ADD: on docker

Containers are orchestrated through Docker-Compose allowing the entire platform: webservers, databases, and task workers, to be easily replicated by other researchers.
Everything is compartmentalized within separate Docker containers where the front-end is networked, through Docker-Compose, to the back-end webserver.

(see Figure \ref{fig-docker})

@@

Docker integration ensures that software dependencies, which typically must be manually installed \cite{doi:10.1093/bioinformatics/btu153,laing2010pan,inouye2014srst2,naccache2014cloud}, are handled automatically.

>>>>

The Spfy platform depends on a series of webservers, databases, and task workers and uses \url{https://www.docker.com/}, a virtualization software package, to run self-contained operating systems on the same host computer.
Software packages are installed within the conatiners and the entire platform is networked together using Docker-Compose \url{https://docs.docker.com/compose/}.
(see Figure \ref{fig-docker})
Docker integration ensures that software dependencies, which typically must be manually installed \cite{doi:10.1093/bioinformatics/btu153,laing2010pan,inouye2014srst2,naccache2014cloud}, are handled automatically and that runtimes in one service are separated from another service.

@@
